---
title: "Supported Geographies"
---

```{r}
#| include: false
library(readxl)
library(gt)

tbl_opts <- function(x) {
  tab_options(
    x,
    table.align = "left",
    table.font.names = "Source Sans Pro",
    footnotes.marks = "standard",
    footnotes.spec_ref = "^",
    footnotes.spec_ftr = "^",
    column_labels.font.weight = "bold"
  ) 
}
```

# Geographies

getcensus supports most, but not all, geographies supported by the Census Bureau API.[^1] Users who are requesting data for multiple years should be aware that ACS geography definitions may change between years; see [ACS Table & Geography Changes](https://www.census.gov/programs-surveys/acs/technical-documentation/table-and-geography-changes.html) on the Census Bureau website.

[^1]: For access to all geographies and geographic components on the Census Bureau API, try the [censusapi](https://ideas.repec.org/c/boc/bocode/s458618.html) Stata package by Jesse Wursten.

A list of geographies supported by getcensus can be found below. For some geographies, users may specify an abbreviation rather than the full name. The Options column indicates whether `statefips()` or `countyfips()` may be specified with a given geography. Bold indicates the option is required with a given geography.

```{r}
#| html-table-processing: none

read_excel(
  "resources/doc_tables.xlsx", 
  sheet = "geographies"
) |>
  gt() |>
  sub_missing(missing_text = "") |>
  fmt_markdown(columns = "Options") |>
  tab_footnote(
    footnote = "only 5-year estimates are available for this geography",
    locations = cells_body(
      columns = Name,
      rows = Name %in% c(
        "county subdivision", 
        "tract", 
        "block group", 
        "zip code tabulation area",
        "state legislative district (upper chamber)",
        "state legislative district (lower chamber)"
      ))
  ) |>
  tab_footnote(
    footnote = md("only 5-year estimates are available when `statefips()` is specified with this geography"),
    locations = cells_body(
      columns = Name,
      rows = Name == "metropolitan statistical area/micropolitan statistical area"
    )
  ) |>
  tbl_opts()

```

# Geographic Components

Geographic components are division of a geographic unit by certain criteria. getcensus does not support all geographic components available on the Census Bureau API.[^2]

[^2]: See [footnote 1](#fn1).

An example: `getcensus [variable IDs], geography(state) geocomponents(H0 C0)` will return two observations for each state: one for the portion of the state not in a metropolitan statistical area ("H0"), and one for the portion of the state in a metropolitan statistical area ("C0").

```{r}
#| html-table-processing: none

read_excel(
  "resources/doc_tables.xlsx", 
  sheet = "geocomponents"
) |>
  gt(groupname_col = "Availability", process_md = TRUE) |>
  tab_footnote(
    footnote = "only 5-year estimates are available for this geographic component",
    locations = cells_body(columns = Code, rows = Code %in% c("89", "95"))
  ) |>
  tab_footnote(
    footnote = "1-year estimates are not avaialble for this geographic component",
    locations = cells_body(columns = Code, rows = Code == "92")
  ) |>
  tbl_opts()

```
