---
title: "Supported Geographies"
---

```{r}
#| include: false
library(readxl)
library(dplyr)
library(stringr)
library(knitr)
library(kableExtra)
options(knitr.kable.NA = "")
options(knitr.table.format = "html")
```

# Geographies

getcensus supports most, but not all, geographies supported by the Census Bureau API.[^1] Users who are requesting data for multiple years should be aware that ACS geography definitions may change between years; see [ACS Table & Geography Changes](https://www.census.gov/programs-surveys/acs/technical-documentation/table-and-geography-changes.html) on the Census Bureau website.

[^1]: For access to all geographies and geographic components on the Census Bureau API, try the [censusapi](https://ideas.repec.org/c/boc/bocode/s458618.html) Stata package by Jesse Wursten.

::: {.callout-warning appearance="simple"}
getcensus does not currently support retrieving 5-year estimates for metropolitan/micropolitan statistical areas if multiple years are requested and 2021 is one of the requested years. This will be fixed in a future release.
:::

A list of geographies supported by getcensus can be found below. For some geographies, users may specify an abbreviation rather than the full name. The Options column indicates whether `statefips()` or `countyfips()` may be specified with a given geography. Bold indicates the option is required with a given geography.

```{r}
read_excel(
  "resources/doc_tables.xlsx", 
  sheet = "geographies", 
  .name_repair = "minimal"
  ) %>%
  rename(" " = 1) %>%
  kable(table.attr = "class='table table-sm'", escape = FALSE) %>%
  footnote(
    symbol = 
      c("only 5-year estimates are available for this geography",
        "only 5-year estimates are available when <code>statefips()</code> is specified with this geography",
        "may not be specified starting with the 2020 5-year estimates (2019 for subject tables)"),
    escape = FALSE
  ) %>%
  column_spec(1, width = "5%")
```

# Geographic Components

Geographic components are division of a geographic unit by certain criteria. getcensus does not support all geographic components available on the Census Bureau API.[^2]

[^2]: See [footnote 1](#fn1).

An example: `getcensus [variable IDs], geography(state) geocomponents(H0 C0)` will return two observations for each state: one for the portion of the state not in a metropolitan statistical area ("H0"), and one for the portion of the state in a metropolitan statistical area ("C0").

```{r geocomponents}
read_excel(
  "resources/doc_tables.xlsx", 
  sheet = "geocomponents", 
  range = cell_cols("A:B") 
) %>%
  kable(
    caption = "Available with <code>geography()</code> <em>us</em>, <em>region</em>, <em>division</em>, or <em>state</em>",
    table.attr = "class='table table-sm' style='width: 100%; '",
    escape = FALSE
  ) 

read_excel(
  "resources/doc_tables.xlsx", 
  sheet = "geocomponents", 
  range = cell_cols("D:F"),
  .name_repair = "minimal"
)  %>%
  rename(" " = 1) %>%
  kable(
    caption = "Available with <code>geography(<em>us</em>)</code> only",
    table.attr = "class='table table-sm' style='width: 100%; xxx'", 
    escape = FALSE
  ) %>%
  footnote(
    symbol = 
      c("only 5-year estimates are available for this geographic component",
        "1-year estimates are not avaialble for this geographic component"),
    escape = FALSE
  )
```
